POMDP comparisons across sigma_m, sigma_g

### 2017-10-21 appendix/appendix.Rmd
WIP policies

```{r aethetics, include=FALSE}
knitr::opts_chunk$set(comment="", message=FALSE)
ggplot2::theme_set(ggplot2::theme_bw())
```

```{r helper_routines, include = FALSE}
det_simulations <- function(x0 = 1/6, Tmax = 20, 
                              B_MSY = K / 2, 
                              F_MSY = r / 2 , 
                              F_PGY = 0.8 * F_MSY){

  msy_policy <- function(x) F_MSY * x
  pgy_policy <- function(x) F_PGY * x
  escapement_policy <- function(x){  ## ASSUMES harvest takes place *after* recruitment
    if(f(x,0) > B_MSY)
      f(x,0) - B_MSY
    else
      0
  }

  # a simulation function
  det_sim <- function(policy, f, x0, Tmax){
    action <- state <- obs <- as.numeric(rep(NA,Tmax))
    state[1] <- x0
    for(t in 1:(Tmax-1)){
      action[t] <- policy(state[t])
      obs[t] <- state[t] - action[t]  # if we observe after harvest but before recruitment
      state[t+1] <- f(state[t], action[t]) 
    }
    data.frame(time = 1:Tmax, state, action, obs)
  }

  # simulate each policy, returning all results in a single unified data frame 
  sims <- 
    list(msy = msy_policy, 
         det = escapement_policy, 
         pgy = pgy_policy) %>% 
    map_df(det_sim, 
           f, x0, Tmax, 
           .id = "method")

@@

@@

```{r}
policies <- list(
  det = map_int(pmax(f(states,0) - S_star,0), ~ which.min(abs(actions - .x))),
  msy = map_int(states, ~ which.min(abs(actions - .x * F_MSY))),
  pgy = map_int(states, ~ which.min(abs(actions - .x * F_PGY))) )
```

@@

>>>>

```{r aethetics, include=FALSE}
knitr::opts_chunk$set(comment="", message=FALSE, cache=TRUE)
ggplot2::theme_set(ggplot2::theme_bw())
```

```{r helper_routines, include = FALSE}
## map cts values to nearest grid indices 
index <- function(x, grid) map_int(x, ~ which.min(abs(.x - grid)))

det_simulations <- function(x0 = 1/6, Tmax = 20, 
                              B_MSY = K / 2, 
                              F_MSY = r / 2 , 
                              F_PGY = 0.8 * F_MSY){

  msy_policy <- function(x) F_MSY * x
  pgy_policy <- function(x) F_PGY * x
  det_policy <- function(x) pmax(f(x,0) - B_MSY,0) ## ASSUMES harvest takes place *after* recruitment
  reed_policy  <- function(x) pmax(x - B_MSY,0) ## Optimal when harvest takes place *before* recruitment, assumes we are seeing a pre-harvest size.
  ## consequently, if we use such a policy when we are seeing a the post-harvest size, we give too much buffer.

  # a simulation function
  det_sim <- function(policy, f, x0, Tmax){
    action <- state <- obs <- as.numeric(rep(NA,Tmax))
    state[1] <- x0
    for(t in 1:(Tmax-1)){
      obs[t] <- state[t]

      action[t] <- policy(obs[t])
      state[t+1] <- f(state[t], action[t]) 
    }
    data.frame(time = 1:Tmax, state, action, obs)
  }

  # simulate each policy, returning all results in a single unified data frame 
  sims <- 
    list(msy = msy_policy, 
         det = det_policy, 
         pgy = pgy_policy
         #opt = reed_policy
         ) %>% 
    map_df(det_sim, 
           f, x0, Tmax, 
           .id = "method")

@@

If we observe->recruit->harvest, $X_{t+1} = f(X_t) - h_t$, then we see the stock right after a harvest and before recuitment, when it is at $X_t ~ $B_{MSY}$.  
If we instead did observe->harvest->recruit, we would see the stock at its pre-harvest size, $X_t ~ B_{MSY} + $H_{MSY}$.

@@

```{r}

policies <- data.frame(
  det = index(pmax(f(states,0) - S_star,0), actions), # assumes obs->recruit->harvest, f(x_t) - h_t
 # det = index(pmax(states - S_star,0),     actions), # assumes obs->harvest->recruit, f(x_t - h_t)
  msy = index(states * F_MSY,               actions),
  pgy = index(states * F_PGY,               actions))
```

@@

Note that when recruitment occurs before harvest, $f(x) - h$, to get to $X_t = B_{MSY}$ as fast as possible, we actually want to harvest a little bit when X is below $B_{MSY}$, so that rather than over-shooting $B_{MSY}$ (deterministic) recruitment would land us right at it $B_{MSY}$.  This corresponds to constant escapement.  The discrete grid makes these appear slightly stepped.

Note that the deterministic solution crosses the MSY solution at an observed value of $B_{MSY}$ (i.e. $K/2 = 0.5$).  PGY harvests are always smaller than MSY harvests, but unlike the deterministic optimal solution, PGY and MSY solutions never go to zero.

```{r}
policy_table <- tibble(state = 1:length(states)) %>%
  bind_cols(policies) %>%
  gather(policy, harvest, -state) %>%
  mutate(harvest = actions[harvest], state = states[state])

policy_table %>% 
  ggplot(aes(state, harvest, col=policy)) + 
  geom_line()  + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8))

Note that when recruitment happens before harvest, escapement is $f(x_t) - h_t$, not $x_t - h_t$.  The effect of a continuous function map $f$ on a discrete grid is also visible as slight wiggles.

```{r}
policy_table  %>%
  mutate(escapement = f(state,harvest))  %>% 
  ggplot(aes(state, escapement, col=policy)) + 
  geom_line() + 
  coord_cartesian(xlim = c(0,K), ylim = c(0, .8))

### Adding the POMDP policy solution
